Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-16 paper.tex
Remove long comment block
Add analysis comment
Add wake spectra figure
Adjust float
Add wake transport totals plotted versus Re
Add placeholder for figure from McMasters and Henderson

\documentclass[energies,article,accept,moreauthors,pdftex,12pt,a4paper]{mdpi}
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, administrativesciences, aerospace, agriculture, agronomy,
% algorithms, animals, antibiotics, antibodies, antioxidants, appliedsciences,
% arts, atmosphere, atoms, axioms, behavioralsciences, bioengineering, biology,
% biomedicines, biomolecules, biosensors, brainsciences, buildings, cancers,
% catalysts, cells, challenges, chemosensors, children, chromatography, climate,
% coatings, computation, computers, cosmetics, crystals, dentistryjournal,
% diagnostics, diseases, diversity, econometrics, economies, education,
% electronics, energies, entropy, environmentalsciences, environments, fibers,
% foods, forests, futureinternet, galaxies, games, genes, geosciences,
% healthcare, humanities, hydrology, informatics, information, inorganics,
% insects, ijerph, ijfs, ijms, ijgi, jcdd, jcm, jdb, jfb, joi, jlpea, jmse,
% jpcg, jpm, jrfm, jsan, land, laws, life, lubricants, machines, marinedrugs,
% materials, mathematics, medicalsciences, membranes, metabolites, metals,
% microarrays, micromachines, microorganisms, minerals, molbank, molecules,
% nanomaterials, ncrna, nutrients, pathogens, pharmaceuticals, pharmaceutics,
% pharmacy, photonics, plants, polymers, processes, proteomes, publications,
% religions, remotesensing, resources, risks, robotics, sensors, socialsciences,
% societies, sports, sustainability, symmetry, systems, technologies, toxics,
% toxins, vaccines, veterinarysciences, viruses, water
%---------
% article
%---------
% The default type of manuscript is article, but could be replaced by using one
% of the class options:
% article, review, communication, commentary, bookreview, correction, addendum,
% editorial, changes, supfile, casereport, comment, conceptpaper,
% conferencereport, meetingreport, discussion, essay, letter, newbookreceived,
% opinion, projectreport, reply, retraction, shortnote, technicalnote, creative
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office
% when the paper is accepted. This will only make changes to the frontpage (e.g.
% the logo of the journal will get visible), the headings, and the copyright
% information. Journal info and pagination for accepted papers will also be
% assigned by the Editorial Office.
% Please insert a blank line is before and after all equation and eqnarray
% environments to ensure proper line numbering when option submit is chosen
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used.
% Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option "pdftex" is for use with pdfLaTeX only. If eps figure are used, use
% the optioin "dvipdfm", with LaTeX and dvi2pdf only.

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2015}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to
%arXiv.org
%\pdfoutput=1

@@

@@

\subsubsection{Mean Momentum Transport}

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

@@

\subsubsection{Mean Kinetic Energy Transport}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

>>>>

\documentclass[energies,article,accept,moreauthors,pdftex,12pt,a4paper]{mdpi}

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2015}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to
% arXiv.org
%\pdfoutput=1

@@

\begin{figure}[ht]
\caption{Airfoil lift to drag ratio as a function of Reynolds number, from 
\cite{McMasters1980}.}
\end{figure}

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Wake spectra at $z/H=0.25$, $y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

\subsubsection{Mean Momentum and Kinetic Energy Transport}

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/mom_bar_graph}
\caption{Momentum transport quantities.}
\label{fig:mom-bar-graph}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{Mean kinetic energy transport quantities.}
\label{fig:K-bar-graph}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/wake_trans_totals}
\caption{Normalized transport totals from Figures~\ref{fig:mom-bar-graph} and 
\ref{fig:K-bar-graph} plotted versus Reynolds number.}
\label{fig:wake-trans-totals}
\end{figure}
